---
title: "Number of Marriages over time in Toronto"
subtitle: "An in depth analysis of marriage"
author: 
  - Robert Ford
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)

data <- read_csv(here::here ("data/analysis_data/analysis_data.csv"))


```


# Introduction

This is all about marriages in Toronto

# Data {#sec-data}

Our data details marriage certificates issued from 2011 to 2024, from @opendatatoronto.

```{r}
#| label: fig-marriage
#| fig-cap: Marriage Licences Issued Over Time
#| echo: false

data |>
  ggplot(aes(x=date, y = marriage_licenses)) +
  geom_point(color = "blue", size =2)+
  labs(
    title = "Marriage Licences Issued Over Time",
    x = "Date",
    y = "Number of Marriage Licences") +
  theme_minimal()
```

You can see that the number of marriages is increasing year over year. Sadly I have read that divorce rates are also on the rise [TODO INSERT SOURCE]

# Discussion

## First discussion point {#sec-first-point}

From this elaborate paper we can tell that marriages are becoming more common. It would be interesting to explore whether this is a larger portion of the population is getting married, or if individuals are marrying more times.


\newpage



# References


